---
title: "p8105 hw5"
author:  "Alexey Abramov"
date: "11/15/2020"
output: 
  github_document:
    toc: true
---

# Setup

```{r, setup}
library(tidyverse)
library(readr)
library(rvest)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 6,
  out.width = "90%"
)

theme_set(
  ggthemes::theme_fivethirtyeight() + theme(legend.position = "bottom")
  )

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.colour = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Loading the data.

```{r}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",)
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

## Summarizing the data to create two new columns for total murders and unsolved murders.  

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

## Performing a prop.test for one city.  

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>%
    pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% 
    pull(hom_total)) %>% 
  broom::tidy()
```

## Now will iterate to the remaining cities.  

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

## Plotting results

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

# Describing the data

```{r}

```


## Problem 2 ideas …

import one dataset

``` r
data_1 = read_csv("lda_data/con_01.csv")
```

    ## Parsed with column specification:
    ## cols(
    ##   week_1 = col_double(),
    ##   week_2 = col_double(),
    ##   week_3 = col_double(),
    ##   week_4 = col_double(),
    ##   week_5 = col_double(),
    ##   week_6 = col_double(),
    ##   week_7 = col_double(),
    ##   week_8 = col_double()
    ## )

``` r
path_df = 
  tibble(
    path = list.files("lda_data"),
  ) %>% 
  mutate(
    path = str_c("lda_data/", path),
    data = map(.............))
```

    ## Error: Problem with `mutate()` input `data`.
    ## x argument ".f" is missing, with no default
    ## ℹ Input `data` is `map(.............)`.

``` r
read_csv(path_df$path[[1]])
```

    ## Error in is.connection(x): object 'path_df' not found

